### 2017-01-19 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Changed date on gas burner report

\vspace*{2\baselineskip}
October 2016}

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (October 2016) \\
CODEN: NTNOEF }

>>>>

\vspace*{2\baselineskip}
January 2017}

@@

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (January 2016) \\
CODEN: NTNOEF }
